E1 Testing - Bayesian Mixed Models

### 2023-08-11 Analysis/e1_brms_test.qmd
brms updates

@@

modelName <- "e1_testDist_uneq"
e1_testDist_uneq <- brm(bf(dist ~ condit,sigma~condit),data=test,file=paste0(here::here("data/model_cache",modelName)))
brms_eq_tidy_uneq <-tidyMCMC(e1_testDist_uneq, conf.int = TRUE, conf.level = 0.95,
           estimate.method = "median", conf.method = "HPDinterval")
brms_eq_tidy_uneq %>%
  mutate_at(vars(estimate, std.error, conf.low, conf.high),
            funs(ifelse(str_detect(term, "sigma"), exp(.), .)))

@@

brm(dist ~ (0+vb)+(1+condit),data=test)

@@

>>>>

```{r}
#| results: asis

#Example of predictor_to_label data frame:
predictor_to_label <- data.frame(
predictor  = c("Intercept","vb350M550",
               "vb600M800", "vb800M1000",
               "vb1000M12000", "vb1200M1400"),
label = c("{\\sc Intercept}", "{\\sc Prime Structure}",
          "{\\sc Target-Message Bias}", "{\\sc Meaning Accuracy}",
          "{\\sc Syntactic Accuracy}", "{\\sc Input}")
)
kf = brmsfit_to_df(e1_testDistRF,predictor_to_label)
kf

table_caption <- paste0(
  "Summary of the fixed effects in the Bayesian logistic mixed-effects model (N = ", 
  nrow(e1_testDistRF$data), ") for Experiment 1.")

print(xtable::xtable(kf, align=c("l", "l", "r", "r", "r"), 
             caption =  table_caption,type="html"), 
      include.rownames=FALSE, sanitize.text.function = function(x){x})
```

@@

modelName <- "e1_testDist_uneq"

e1_testDist_uneq <- brm(bf(dist ~ condit,sigma~condit),data=test,file=paste0(here::here("data/model_cache",modelName)))

brms_eq_tidy_uneq <-tidyMCMC(e1_testDist_uneq, conf.int = TRUE, conf.level = 0.95,
           estimate.method = "median", conf.method = "HPDinterval")

brms_eq_tidy_uneq |> mutate_at(vars(estimate, std.error, conf.low, conf.high),
            funs(ifelse(str_detect(term, "sigma"), exp(.), .)))

@@

#brm(dist ~ (0+vb)+(1+condit),data=test)

@@

plot(e1_testDistRF2_0,"^b_")
pp_check(e1_testDistRF2_0, type= "loo_pit")
plot(conditional_effects(egt_rf_vb),points=FALSE)
plot(conditional_effects(e1_testDistRF2_0),points=FALSE
pp_check(egt5k,type = "stat_2d")
pp_check(egt5k,type = "scatter_avg")
pp_check(egt5k,type = "error_hist")
pp_check(egt5k,type = "ribbon_grouped", group="vb")
pp_check(egt5k,type = "stat_grouped", group="vb",ndraws=150)
